### 2021-11-10 manuscript.Rmd
Revises text and analysis
- Removes unneeded sections
- Switches to Type 2 SS

---
title             : "Biased estimates of implicit and explicit learning in applications of the process-dissociation procedure to the SRT task"
shorttitle        : "Biased PD estimates in sequence learning"

@@

Implicit learning refers to the ability to adapt to regularities inherent in the environment in the absence of conscious awareness about the ongoing learning process itself or about the outcome of what is learned. 
This ability is fundamental for human beings as it allows us to act optimally in stable environments with relatively little effort.

@@

In their application to sequence learning, @destrebecqz_can_2001 used a generation task:
After SRTT training, participants are asked to generate a sequence of responses that is either as similar as possible to the learned sequence (in the inclusion condition), or a sequence as dissimilar as possible (exclusion condition).
To the degree that explicit knowledge is available, the proportion of generated responses that match the learned sequence should differ between inclusion and exclusion.
To the degree that implicit knowledge is available, the proportion of matching responses in the exclusion condition should be greater than a chance baseline or control condition.
In one group (i.e., RSI = 0 ms), participants were better than chance in their ability to reproduce the regularity in the sequence, even under exclusion instructions (i.e., performance under exclusion condition, $E$, was above a chance baseline $B$, $E>B$), a finding that was interpreted as reflecting sequence knowledge.
However, performance under inclusion ($I$) and exclusion instructions was identical (i.e., $I=E$), a finding that is interpreted as indicating the absence of explicit knowledge and instead suggests that the sequence knowledge was fully implicit.[^control-sequence-designs]

[^control-sequence-designs]:
Note that the $E>B$ pattern could not be replicated in other studies [@wilkinson_intentional_2004; @norman_fringe_2006] that, as a baseline, compared generation performance with that for a *control sequence* instead of an a-priori fixed value.

@@

out.perm <- apa_print(
  aov_ez(data = tmp.perm, dv = "SRI", within = c("block", "frequency"), id = "id")
)

@@

out <- apa_print(
  aov_ez(data = tmp, dv = "SRI", id = "id", between = "material", within = "block")
)
```

@@

# ANOVA for complete design
out <- apa_print(
  aov_ez(data = tmp2, id = "id", dv = "correct_SOC", between = c("material", "generation", "order"), within = "PD_instruction")
)

# separate analysis for free-generation task
tmp.a <- tmp2[tmp2$generation == "Free", ]
out.a <- apa_print(
  aov_ez(data = tmp.a, id = "id", dv = "correct_SOC", between = c("material", "order"), within = "PD_instruction")
)

# Post-hoc paired comparisons for free-generation group
fit <- aov_ez(data = tmp.a, id = "id", dv = "correct_SOC", between = c("material", "order"), within = "PD_instruction")
tukey <- apa_print(pairs(emmeans(fit, specs = "material"), adjust = "tukey"))
```

@@

# ANOVA for full design
model <- aov_ez(data = tmp, id = "id", dv = "was_cue", between = c("material", "order"), within = "PD_instruction")
out <- apa_print(model)

@@

# analyse blocks separately (extract only `full_result` to output object)
out_1st <- apa_print(
  aov_ez(data = tmp[tmp$block == "first", ], id = "id", dv = "was_cue", between = c("material", "PD_instruction"))
)$full_result

out_2nd <- apa_print(
  aov_ez(data = tmp[tmp$block == "second",], id = "id", dv = "was_cue", between = c("material","PD_instruction"))
)$full_result
```

>>>>

---
title             : "Distorted estimates of implicit and explicit learning in applications of the process-dissociation procedure to the SRT task"
shorttitle        : "Distorted PD estimates in sequence learning"

@@

@@

In their application to sequence learning, @destrebecqz_can_2001 used a generation task:
After SRTT training, participants are asked to generate a sequence of responses that is either as similar as possible to the learned sequence (in the inclusion condition), or a sequence as dissimilar as possible (exclusion condition).
To the degree that explicit knowledge is available, the proportion of generated responses that match the learned sequence should differ between inclusion and exclusion.
To the degree that implicit knowledge is available, the proportion of matching responses in the exclusion condition should be greater than a chance baseline or control condition.
In one group (i.e., RSI = 0 ms), participants were better than chance in their ability to reproduce the regularity in the sequence, even under exclusion instructions (i.e., performance under exclusion condition, $E$, was above a chance baseline $B$, $E>B$), a finding that was interpreted as reflecting sequence knowledge.
However, performance under inclusion ($I$) and exclusion instructions was identical (i.e., $I=E$), a finding that is interpreted as indicating the absence of explicit knowledge and instead suggests that the sequence knowledge was fully implicit.

@@

out.perm <- apa_print(
  aov_ez(data = tmp.perm, dv = "SRI", within = c("block", "frequency"), id = "id", type = 2)
)

@@

out <- apa_print(
  aov_ez(data = tmp, dv = "SRI", id = "id", between = "material", within = "block", type = 2)
)
```

@@

# ANOVA for complete design
out <- apa_print(
  aov_ez(data = tmp2, id = "id", dv = "correct_SOC", between = c("material", "generation", "order"), within = "PD_instruction", type = 2)
)

# separate analysis for free-generation task
tmp.a <- tmp2[tmp2$generation == "Free", ]
out.a <- apa_print(
  aov_ez(data = tmp.a, id = "id", dv = "correct_SOC", between = c("material", "order"), within = "PD_instruction", type = 2)
)

# Post-hoc paired comparisons for free-generation group
fit <- aov_ez(data = tmp.a, id = "id", dv = "correct_SOC", between = c("material", "order"), within = "PD_instruction", type = 2)
tukey <- apa_print(pairs(emmeans(fit, specs = "material"), adjust = "tukey"))
```

@@

# ANOVA for full design
model <- aov_ez(data = tmp, id = "id", dv = "was_cue", between = c("material", "order"), within = "PD_instruction", type = 2)
out <- apa_print(model)

@@

# analyse blocks separately (extract only `full_result` to output object)
out_1st <- apa_print(
  aov_ez(data = tmp[tmp$block == "first", ], id = "id", dv = "was_cue", between = c("material", "PD_instruction"), type = 2)
)$full_result

out_2nd <- apa_print(
  aov_ez(data = tmp[tmp$block == "second",], id = "id", dv = "was_cue", between = c("material","PD_instruction"), type = 2)
)$full_result
```
